Self-Supervised Learning of Generalized Policies in adversarial domains

### 2021-05-27 doc/paper/paper.tex
doc changes

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
(A) Num[cell-has-martian] [k=1]
(B) Bool[cell-has-target_martian] [k=1]
(C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]
\end{Verbatim}

@@

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Num[cell-has-martian] [k=1]
  (B) Bool[cell-has-target_martian] [k=1]
  (C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]
\end{Verbatim}

@@

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]
  (B) Bool[And(row-hv-AGENT,Exists(adjacent_row,row-hv-TARGET))] [k=5]
  (C) Dist[row-hv-AGENT;adjacent_row;row-hv-TARGET] [k=4]
  (D) Dist[col-hv-TARGET;adjacent_col;col-hv-AGENT] [k=4]
\end{Verbatim}

@@

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Num[And(cell-has-token,Exists(left_cell,cell-has-token))] [k=5]
  (B) Num[And(cell-has-token,Forall(leftdown_cell,cell-has-token))] [k=5]
  (C) Num[And(cell-has-token,Forall(rightdown_cell,cell-has-token))] [k=5]

@@

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Atom[holding_pet] [k=1]
  (B) Bool[And(cell-has-agent,Exists(adjacent_cell,cell-has-destiny))] [k=5]
  (C) Dist[cell-has-agent;adjacent_cell;cell-has-destiny] [k=4]
  (D) Dist[cell-has-agent;adjacent_cell;cell-has-pet] [k=4]
\end{Verbatim}

>>>>

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
(A) Num[cell-has-martian] [k=1]:
number of martians

(B) Bool[cell-has-target_martian] [k=1]:
there is some target martian

(C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]:
absolute horizontal distance between agent and target martian
\end{Verbatim}

@@

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Num[cell-has-martian] [k=1]:
  number of martians

  (B) Bool[cell-has-target_martian] [k=1]:
  there is one target martian

  (C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]:
  absolute horizontal distance between agent and target martian
\end{Verbatim}

@@

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]:
  the column of the agent is adjacent to the column of the adversary

  (B) Bool[And(row-hv-AGENT,Exists(adjacent_row,row-hv-TARGET))] [k=5]:
  the row of the agent is adjacent to the row of the adversary

  (C) Dist[row-hv-AGENT;adjacent_row;row-hv-TARGET] [k=4]:
  absolute vertical distance between agent and adversary

  (D) Dist[col-hv-TARGET;adjacent_col;col-hv-AGENT] [k=4]:
  absolute horizontal distance between agent and adversary
\end{Verbatim}

@@

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Num[And(cell-has-token,Exists(left_cell,cell-has-token))] [k=5]:
  number of tokens with a token immediately to the left of it

  (B) Num[And(cell-has-token,Forall(leftdown_cell,cell-has-token))] [k=5]:
  number of tokens with a token immediately to the leftdown of it

  (C) Num[And(cell-has-token,Forall(rightdown_cell,cell-has-token))] [k=5]:
  number of tokens with a token immediately to the rightdown of it

@@

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Atom[holding_pet] [k=1]:
  the agent is holding the pet

  (B) Bool[And(cell-has-agent,Exists(adjacent_cell,cell-has-destination))] [k=5]:
  the destination is adjacent to the agent

  (C) Dist[cell-has-agent;adjacent_cell;cell-has-destination] [k=4]:
  manhattan distance between agent and destination

  (D) Dist[cell-has-agent;adjacent_cell;cell-has-pet] [k=4]:
  manhattan distance between agent and pet
\end{Verbatim}
